My Findings

### 2024-08-30 Findings (Shared Folder)/Chapters/MolecularBiology.tex
new notes added

>>>>

	\item Natural and man-made transport webs are frequently dominated by dense sets of nested cycles. The architecture of these networks, as defined by the topology and edge weights, determines how efficiently the networks perform their function. \cite{Modes2016}
	\item For many purposes, e.g., when analyzing blood flow in arteries, the dependence of viscosity on shear rate can be neglected and blood can be treated as a Newtonian fluid as defined above \cite{Secomb2021}.
	 the apparent viscosity in large vessels matches the in vitro result, but the apparent viscosity is substantially higher than the in vitro estimate in smaller vessels. For example, the estimated apparent viscosity in a $7\mu m$ capillary at hematocrit $45$ percent is about $8.4\mu_p$, almost seven times higher than would be expected based on data from glass tubes.
